Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2018-01-03 manuscript-md/index.Rmd
Address Niinemets comments on introduction

* We developed a hierarchical multivariate Bayesian model that assumes separate means and covariance structures within and across PFTs and fit this model to seven leaf traits from the TRY database: longevity, specific leaf area, nitrogen and phosphorus contents, and rates of dark respiration, maximum Rubisco carboxylation, and maximum electron transport. 
We evaluated the ability of this model to estimate trait means and reproduce leaf economic trade-offs.

* Trait correlations were generally consistent in direction within and across PFTs, and consistent with predictions of the leaf economic spectrum.
However, correlation strength varied substantially across PFTs indicating that leaf economic relationships within PFTs are often confounded by other biotic and abiotic factors.

>>>>

* We developed a hierarchical multivariate Bayesian model that assumes separate means and covariance structures within and across PFTs and fit this model to seven leaf traits from the TRY database: longevity, specific leaf area, nitrogen content, phosphorus content, dark respiration rate, maximum photosynthetic carboxylation rate ($V_{c,max}$), and maximum photosynthetic electron transport rate ($J_{max}$). 
We evaluated the ability of this model to estimate trait means and reproduce leaf economic trade-offs.

* Trait correlations were generally consistent in direction within and across PFTs, and consistent with predictions of the leaf economic spectrum.
However, correlation strength varied substantially across PFTs indicating that leaf economic relationships within PFTs are often confounded by the unique physiology of certain plant types or environmental conditions in certain biomes.
